Opt-K

### 2013-03-12 paper/paper.tex
math better
3sigma
two eqs on same line

Therefore, the most appropriate emmision distribution for discrete state
MSMs is that of the uniform distribution over the phase-space volume of
the state. That is, the likelihood of observing a conformation in phase
space given that the conformation is assigned to state $i$ is $0$
if the conformation is outside of the bounding volume of the state and
constant if the conformation is within the volume. The constant is set
so that the distribution integrates to $1$, and is thus the reciprocal
volume of the microstate.

@@

Now, we sample random points from the uniform distribution over the
bounding box. We check these points against all of the gaussian PDFs. If
the point is farther than \texttt{3-sigma} away from every cluster
center, we reject it, reasoning that it is probably outside the convex
hull. The remaining points are now a representation of the uniform
distribution over the convex hull of phase space. For each point, we
compute its distance to each of the cluster centers, ``assigning'' it to
the center it is closest to. As the number of randomly sampled points
goes to infinity, the fraction of the points assigned to each state
converges to being proportional to the state's volume.

>>>>

Therefore, the most appropriate emission distribution for discrete state
MSMs is that of the uniform distribution over the phase-space volume of
the state. That is, the likelihood of observing a conformation in phase
space given that the conformation is assigned to state $i$ is $0$
if the conformation is outside of the bounding volume of the state and
constant if the conformation is within the volume. The constant is set
so that the distribution integrates to $1$, and is thus the reciprocal
volume of the microstate.

@@

Now, we sample random points from the uniform distribution over the
bounding box. We check these points against all of the gaussian PDFs. If
the point is farther than $3\sigma$ away from every cluster
center, we reject it, reasoning that it is probably outside the convex
hull. The remaining points are now a representation of the uniform
distribution over the convex hull of phase space. For each point, we
compute its distance to each of the cluster centers, ``assigning'' it to
the center it is closest to. As the number of randomly sampled points
goes to infinity, the fraction of the points assigned to each state
converges to being proportional to the state's volume.
